---
title: "Maya's Design Kit"
output: 
  html_document:
    css: styles.css
vignette: >
  %\VignetteIndexEntry{design_kit}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE}
library(designkit)
```

## {.tabset}

### Buttons

#### Primary Button

```{r, eval=FALSE}
primary_btn("primary", "TEXT")
primary_btn("primary", "TEXT", disabled = TRUE)
```

```{r, echo=FALSE}
primary_btn("primary", "TEXT")
primary_btn("primary", "TEXT", disabled = TRUE)
```

#### Secondary Button

```{r, eval=FALSE}
secondary_btn("secondary", "TEXT")
secondary_btn("secondary", "TEXT", disabled = TRUE)
```

```{r, echo=FALSE}
secondary_btn("secondary", "TEXT")
secondary_btn("secondary", "TEXT", disabled = TRUE)
```

### Icon Button 

```{r, eval=FALSE}
icon_btn("icon", "calendar")
icon_btn("icon", "calendar", disabled = TRUE)
```

```{r, echo=FALSE}
icon_btn("icon", "calendar")
icon_btn("icon", "calendar", disabled = TRUE)
```

### Textfield

```{r, eval=FALSE}
text_input("test", "test")
text_input("test", "test", disabled = TRUE)
```

```{r, echo=FALSE}
text_input("test", "test")
text_input("test", "test", disabled = TRUE)
```

### Tab Bar

```{r, eval=FALSE}
tab_wrapper(
  tab("TAB", ""),
  tab("TAB", ""),
  tab("TAB", "")
)
```


```{r, echo=FALSE}
htmltools::HTML('<div class="Panel">
	<nav>
		<ul class="Tabs">
			<li class="Tabs__tab active Tab"><a href="#">TAB</a></li>
			<li class="Tabs__tab Tab"><a href="#">TAB</a></li>
			<li class="Tabs__tab Tab"><a href="#">TAB</a></li>
			<li class="Tabs__presentation-slider" role="presentation"></li>
		</ul>
	</nav>
</div>')
```

<script>
var tabs = document.getElementsByClassName('Tab');

Array.prototype.forEach.call(tabs, function(tab) {
	tab.addEventListener('click', setActiveClass);
});

function setActiveClass(evt) {
	Array.prototype.forEach.call(tabs, function(tab) {
		tab.classList.remove('active');
	});
	
	evt.currentTarget.classList.add('active');
}
</script>

<style>
 .Panel__body {
	 background-color: #f2f2f2;
	 padding: 10px 20px;
}
 .Tabs {
	 position: relative;
	 background-color: #fff;
	 margin: 0;
	 padding: 0;
	 list-style: none;
	 width: max-content;
}
 .Tabs:after {
	 content: ' ';
	 display: table;
	 clear: both;
}
 .Tabs__tab {
	 float: left;
	 width: 33.333%;
	 text-align: center;
}
 .Tabs__tab:first-child.active ~ .Tabs__presentation-slider {
	 transform: translateX(0) scaleX(0.333);
}
 .Tabs__tab:nth-child(2).active ~ .Tabs__presentation-slider {
	 transform: translateX(33.333%) scaleX(0.333);
}
 .Tabs__tab:nth-child(3).active ~ .Tabs__presentation-slider {
	 transform: translateX(calc(33.333% * 2)) scaleX(0.333);
}
 .Tabs__presentation-slider {
	 position: absolute;
	 bottom: 0;
	 left: 0;
	 width: 100%;
	 height: 2px;
	 background-color: var(--primary);
	 transform-origin: 0 0;
	 transition: transform 0.25s;
}
 .Tab {
	 font-weight: 600;
}

 .Tab > a {
	 display: block;
	 padding: 10px 12px;
	 text-decoration: none;
	 color: darkgray;
	 transition: color 0.15s;
}
 .Tab.active > a {
	 color: var(--primary);
	 text-decoration: none;
}
 .Tab:hover > a {
	 color: var(--primary);
	 background-color: var(--secondary);
	 text-decoration: none;
}
</style>

### Tooltip

```{r}
tooltip_element("wrapper-id", 
                icon_btn("search", icon = "search"),
                "Lorem ipsum")
```