---
title: "Maya's Design Kit"
output: 
  html_document:
    css: styles.css
---

```{r, echo=FALSE}
library(designkit)
```

<div class="github-icon"><a href="https://github.com/MayaGans/my_designkit"><svg class="github-svg" xmlns="http://www.w3.org/2000/svg" width="24" height="24" viewBox="0 0 24 24"><path d="M12 0c-6.626 0-12 5.373-12 12 0 5.302 3.438 9.8 8.207 11.387.599.111.793-.261.793-.577v-2.234c-3.338.726-4.033-1.416-4.033-1.416-.546-1.387-1.333-1.756-1.333-1.756-1.089-.745.083-.729.083-.729 1.205.084 1.839 1.237 1.839 1.237 1.07 1.834 2.807 1.304 3.492.997.107-.775.418-1.305.762-1.604-2.665-.305-5.467-1.334-5.467-5.931 0-1.311.469-2.381 1.236-3.221-.124-.303-.535-1.524.117-3.176 0 0 1.008-.322 3.301 1.23.957-.266 1.983-.399 3.003-.404 1.02.005 2.047.138 3.006.404 2.291-1.552 3.297-1.23 3.297-1.23.653 1.653.242 2.874.118 3.176.77.84 1.235 1.911 1.235 3.221 0 4.609-2.807 5.624-5.479 5.921.43.372.823 1.102.823 2.222v3.293c0 .319.192.694.801.576 4.765-1.589 8.199-6.086 8.199-11.386 0-6.627-5.373-12-12-12z"/></svg></a></div>

## {.tabset}

### Buttons

#### Primary Button

```{r, eval=FALSE}
primary_btn("primary", "TEXT")
primary_btn("primary", "TEXT", disabled = TRUE)
```

```{r, echo=FALSE}
primary_btn("primary", "TEXT")
primary_btn("primary", "TEXT", disabled = TRUE)
```

#### Secondary Button

```{r, eval=FALSE}
secondary_btn("secondary", "TEXT")
secondary_btn("secondary", "TEXT", disabled = TRUE)
```

```{r, echo=FALSE}
secondary_btn("secondary", "TEXT")
secondary_btn("secondary", "TEXT", disabled = TRUE)
```

### Icon Button 

```{r, eval=FALSE}
icon_btn("icon", "calendar")
icon_btn("icon", "calendar", disabled = TRUE)
```

```{r, echo=FALSE}
icon_btn("icon", "calendar")
icon_btn("icon", "calendar", disabled = TRUE)
```

### Textfield

```{r, eval=FALSE}
text_input("test", "test")
text_input("test", "test", disabled = TRUE)
```

```{r, echo=FALSE}
text_input("test", "test")
text_input("test", "test", disabled = TRUE)
```

### Tab Bar

```{r, eval=FALSE}
tab_wrapper(
  tab("TAB", ""),
  tab("TAB", ""),
  tab("TAB", "")
)
```


```{r, echo=FALSE}
htmltools::HTML('<div class="Panel">
	<nav>
		<ul class="Tabs">
			<li class="Tabs__tab active Tab"><a href="#">TAB</a></li>
			<li class="Tabs__tab Tab"><a href="#">TAB</a></li>
			<li class="Tabs__tab Tab"><a href="#">TAB</a></li>
			<li class="Tabs__presentation-slider" role="presentation"></li>
		</ul>
	</nav>
</div>')
```

<script>
var tabs = document.getElementsByClassName('Tab');

Array.prototype.forEach.call(tabs, function(tab) {
	tab.addEventListener('click', setActiveClass);
});

function setActiveClass(evt) {
	Array.prototype.forEach.call(tabs, function(tab) {
		tab.classList.remove('active');
	});
	
	evt.currentTarget.classList.add('active');
}
</script>

<style>
 .Panel__body {
	 background-color: #f2f2f2;
	 padding: 10px 20px;
}
 .Tabs {
	 position: relative;
	 background-color: #fff;
	 margin: 0;
	 padding: 0;
	 list-style: none;
	 width: max-content;
}
 .Tabs:after {
	 content: ' ';
	 display: table;
	 clear: both;
}
 .Tabs__tab {
	 float: left;
	 width: 33.333%;
	 text-align: center;
}
 .Tabs__tab:first-child.active ~ .Tabs__presentation-slider {
	 transform: translateX(0) scaleX(0.333);
}
 .Tabs__tab:nth-child(2).active ~ .Tabs__presentation-slider {
	 transform: translateX(33.333%) scaleX(0.333);
}
 .Tabs__tab:nth-child(3).active ~ .Tabs__presentation-slider {
	 transform: translateX(calc(33.333% * 2)) scaleX(0.333);
}
 .Tabs__presentation-slider {
	 position: absolute;
	 bottom: 0;
	 left: 0;
	 width: 100%;
	 height: 2px;
	 background-color: var(--primary);
	 transform-origin: 0 0;
	 transition: transform 0.25s;
}
 .Tab {
	 font-weight: 600;
}

 .Tab > a {
	 display: block;
	 padding: 10px 12px;
	 text-decoration: none;
	 color: darkgray;
	 transition: color 0.15s;
}
 .Tab.active > a {
	 color: var(--primary);
	 text-decoration: none;
}
 .Tab:hover > a {
	 color: var(--primary);
	 background-color: var(--secondary);
	 text-decoration: none;
}
</style>

### Tooltip

```{r}
tooltip_element("wrapper-id", 
                icon_btn("search", icon = "search"),
                "Lorem ipsum")
```